---
title: "r-week-8-hw-eeb177.Rmd"
author: "Jin Sun Kim"
date: "March 7, 2017"
output: html_document
---
HW 8 
Part 1
#6.

```{r}
library(ggplot2)
setwd("/home/eeb177-student/Desktop/eeb-177/Homework/")
canids <- read.csv("canid-ranges.csv", header = F, as.is = T)
names(canids) <- c("genus", "species", "minage", "maxage")
head(canids)

canid_occ <- ggplot(canids, aes( species, ymin = maxage, ymax=minage, colour = genus))
canid_occ <- canid_occ + geom_linerange()
canid_occ

canid_occ <- canid_occ + theme(legend.position="none")
canid_occ

canid_occ <- canid_occ + coord_flip()
canid_occ

canid_occ <- canid_occ +  theme(axis.text.y = element_text(size=3))
canid_occ

canid_occ <- canid_occ + theme(axis.ticks.y=element_blank())
canid_occ

canid_occ <- canid_occ + scale_y_continuous(limits=c(0, 40), expand = c(0, 0), breaks=c(0, 10, 20, 30, 40))
canid_occ

canid_occ <- canid_occ + labs(title = "Canid Fossil Occurrences", x = "Species", y = "Ma ago") + theme(plot.title = element_text(hjust = 0.5, size=22, face = "bold"), axis.title =element_text(size=20))
canid_occ

ggsave(filename = "canid-occ.pdf", plot = canid_occ)
```

#7.
The occurrences of the species of canids are displayed in this figure.

There are 211 unique fossil species contained within the figure.

There are 46 unique fossil genera.

The species Canidae has the longest fossil range.

#8.
Repeating Part 1b with the clade Aves

```{r}
library(ggplot2)
setwd("/home/eeb177-student/Desktop/eeb-177/Homework/")
Aves <- read.csv("Aves-ranges.csv", header = F, as.is = T)
names(Aves) <- c("genus", "species", "minage", "maxage")

Aves_occ <- ggplot(Aves, aes( species, ymin = maxage, ymax=minage, colour = genus))
Aves_occ <- Aves_occ + geom_linerange()
Aves_occ <- Aves_occ + theme(legend.position="none")
Aves_occ <- Aves_occ + coord_flip()
Aves_occ <- Aves_occ +  theme(axis.text.y = element_text(size=2))
Aves_occ <- Aves_occ + theme(axis.ticks.y=element_blank())
Aves_occ <- Aves_occ + scale_y_continuous(limits=c(0, 140), expand = c(0, 0), breaks=c(0, 30, 60, 90, 120))
Aves_occ <- Aves_occ + labs(title = "Canid Fossil Occurrences", x = "Species", y = "Ma ago") + theme(plot.title = element_text(hjust = 0.5, size=22, face = "bold"), axis.title =element_text(size=20))
Aves_occ

ggsave(filename = "Aves-occ.pdf", plot = Aves_occ)
```

The occurrences of the species of the clade Aves are displayed in this figure.

There are 1696 unique fossil species of Aves.

There are 984 unique fossil genera of Aves.

The species Aves has the longest fossil range.


