---
title: "r-week-8-hw-eeb177.Rmd"
author: "Jin Sun Kim"
date: "March 7, 2017"
output: html_document
---
HW 8 
Part 1
#6.

```{r}
library(ggplot2)
setwd("/home/eeb177-student/Desktop/eeb-177/Homework/")
canids <- read.csv("canid-ranges.csv", header = F, as.is = T)
names(canids) <- c("genus", "species", "minage", "maxage")
head(canids)

canid_occ <- ggplot(canids, aes( species, ymin = maxage, ymax=minage, colour = genus))
canid_occ <- canid_occ + geom_linerange()
canid_occ

canid_occ <- canid_occ + theme(legend.position="none")
canid_occ

canid_occ <- canid_occ + coord_flip()
canid_occ

canid_occ <- canid_occ +  theme(axis.text.y = element_text(size=3))
canid_occ

canid_occ <- canid_occ + theme(axis.ticks.y=element_blank())
canid_occ

canid_occ <- canid_occ + scale_y_continuous(limits=c(0, 40), expand = c(0, 0), breaks=c(0, 10, 20, 30, 40))
canid_occ

canid_occ <- canid_occ + labs(title = "Canid Fossil Occurrences", x = "Species", y = "Ma ago") + theme(plot.title = element_text(hjust = 0.5, size=22, face = "bold"), axis.title =element_text(size=20))
canid_occ

ggsave(filename = "canid-occ.pdf", plot = canid_occ)
```

#7.
The occurrences of the species of canids are displayed in this figure.

There are 211 unique fossil species contained within the figure.

There are 46 unique fossil genera.

The species Canidae has the longest fossil range.

#8.
Repeating Part 1b with the clade Aves

```{r}
library(ggplot2)
setwd("/home/eeb177-student/Desktop/eeb-177/Homework/")
Aves <- read.csv("Aves-ranges.csv", header = F, as.is = T)
names(Aves) <- c("genus", "species", "minage", "maxage")

Aves_occ <- ggplot(Aves, aes( species, ymin = maxage, ymax=minage, colour = genus))
Aves_occ <- Aves_occ + geom_linerange()
Aves_occ <- Aves_occ + theme(legend.position="none")
Aves_occ <- Aves_occ + coord_flip()
Aves_occ <- Aves_occ +  theme(axis.text.y = element_text(size=2))
Aves_occ <- Aves_occ + theme(axis.ticks.y=element_blank())
Aves_occ <- Aves_occ + scale_y_continuous(limits=c(0, 140), expand = c(0, 0), breaks=c(0, 30, 60, 90, 120))
Aves_occ <- Aves_occ + labs(title = "Canid Fossil Occurrences", x = "Species", y = "Ma ago") + theme(plot.title = element_text(hjust = 0.5, size=22, face = "bold"), axis.title =element_text(size=20))
Aves_occ

ggsave(filename = "Aves-occ.pdf", plot = Aves_occ)
```

The occurrences of the species of the clade Aves are displayed in this figure.

There are 1696 unique fossil species of Aves.

There are 984 unique fossil genera of Aves.

The species Aves has the longest fossil range.


**Part 2: Data Frames **
1. Exploring Data Frames

```{r}
#Challenge 1.

df <- data.frame(first = c('Jin Sun'),
                 last = c('Kim'),
                 lucky_number = c(7),
                 stringsAsFactors = FALSE)
df <- rbind(df, list('Jung', 'Kim', 10) )
df <- cbind(df, coffeetime = c(TRUE,TRUE))

#Challenge 2.
source(file = "/home/eeb177-student/scripts/lab-9-script.R")

#Challenge 3.
str(gapminder)

#gapminder is a data frame with columns
#country and continent are factors.
#year is an integer vector.
#pop, lifeExp, and gdpPercap are numeric vectors

```

2. Subsetting Data

```{r}
#Challenge 1
x <- c(5.4, 6.2, 7.1, 4.8, 7.5)
names(x) <- c('a', 'b', 'c', 'd', 'e')
print(x)
#1.
x[2:4]
#2.
x[-c(1,5)]
#3.
x[c(2,3,4)]

#Challenge 2
#Answer is A and C

#Challenge 3
x_subset <- x[x<7 & x>4]
print(x_subset)

#Challenge 4
#Answer is D

#Challenge 5
xlist <- list(a = "Software Carpentry", b = 1:10, data = head(iris))

xlist$b[2]

#Challenge 6
mod <- aov(pop ~ lifeExp, data=gapminder)

attributes(mod)
mod$df.residual

#Challenge 7
#1.
gapminder[gapminder$year == 1957,]
#2.
gapminder[,-c(1:4)]
#3.
gapminder[gapminder$lifeExp > 80,]
#4.
gapminder[1, c(4, 5)]
#5.
gapminder[gapminder$year == 2002 | gapminder$year == 2007,]

#Challenge 8
#1.
#Since gapminder is a data.frame, it needs to be subsetted on 2 dimensions. gapminder[1:20, ] subsets the data to give the first 20 rows and all columns.
#2.
gapminder_small <- gapminder[c(1:9, 19:23),]

```

3. Creating Publication Quality Graphics

```{r}
#Challenge 1
ggplot(data = gapminder, aes(x = year, y = lifeExp)) + geom_point()

#Challenge 2
ggplot(data = gapminder, aes(x = year, y = lifeExp, color=continent)) + geom_point()
#life expectancy is greatest in Europe and smallest in Africa

#Challenge 3
ggplot(data = gapminder, aes(x=year, y=lifeExp, by=country)) + geom_point() + geom_line(aes(color=continent))
#the lines now get drawn over  the points

#Challenge 4a
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) + geom_point(size=3, color="orange") + scale_x_log10() + geom_smooth(method="lm", size=1.5)

#Challenge 4b
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp, color = continent)) + geom_point(size=3, pch=17) + scale_x_log10() + geom_smooth(method="lm", size=1.5)

#Challenge 5
ggplot(data = gapminder, aes(x = gdpPercap, fill=continent)) + geom_density(alpha=0.6) + facet_wrap( ~ year) + scale_x_log10()

```
